---
title: "March ACR"
author: "Nick Lauerman"
date: "1 May 2019"
output: 
  pdf_document: 
    fig_caption: yes
    fig_height: 4
    fig_width: 4
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
                               # Update Title and date above and below line 26
knitr::opts_chunk$set(echo = TRUE)
```
# Libraries
```{r}
library(lubridate)
```

# Data
## Variables used
```{r}
month <- "May"                                                # Update Line 208
year <- 2019

```

## Read Data In
The data is a CSV file that is created by saving the ACR tab of the FPA Excel
Workbook.
```{r}
ACR <- read.csv(file = "./data/ACR.csv",
                stringsAsFactors = FALSE)
name <- c("SQA",
          "Application",
          "CRNumber",
          "CRDate",
          "CRApproved",
          "IENumber",
          "IEDate",
          "IEApproved",
          "Reason",
          "Comments")
names(ACR) <- name
rm(name)
```

## Format the Data
### Convert to Factor
```{r}
ACR$SQA <- as.factor(ACR$SQA)
ACR$Application <- as.factor(ACR$Application)
ACR$CRApproved <- as.factor(ACR$CRApproved)
ACR$IEApproved <- as.factor(ACR$IEApproved)
levels(ACR$IEApproved)[1] <- NA
ACR$Reason <- as.factor(ACR$Reason)
levels(ACR$Reason)[1] <- NA
```

### Convert to Dates
```{r}
ACR$CRDate <- as.Date(ACR$CRDate, format = "%d-%b-%y")
ACR$IEDate<- as.Date(ACR$IEDate, format = "%d-%b-%y")
ACR$CRmonth <- lubridate::month(ACR$CRDate, label = TRUE)
ACR$CRyear <- lubridate::year(ACR$CRDate)
ACR$IEmonth <- lubridate::month(ACR$IEDate, label = TRUE)
ACR$IEyear <- lubridate::year(ACR$IEDate)          
```

## Structure of The Data
```{r}
str(ACR)
```

# Metrics
## Select Data
Data is selected first for the Month and Year of interest. The selection is based
on boththe CR and I&E dates. This selelction is used as a master dataframe. Two 
additional dataframes are prduced the first of the approval of the CR inthe month
and the second for the approval of the I&E in the month.
```{r}
#create master dataframe
work <- subset(ACR,
               subset = (CRmonth == month & CRyear == year) |
                    (subset = IEmonth == month & IEyear == year))
# Create the CR data fram
workCR <- subset(ACR,
               subset = CRmonth == month & CRyear == year)
# create the IE data frame.
workIE <- subset(ACR,
               subset = IEmonth == month & IEyear == year)
```

## Counts
### Data Changes (CR) Request Approved
```{r}
nrow(subset(workCR,
            subset = (CRApproved == "A" | CRApproved == "A-FP"))) -
  nrow(subset(workCR,
            subset = (IEApproved == "D")))
```

### Data Change Request Disapproved
```{r}
nrow(subset(workCR,
            subset = (CRApproved == "D")))
```

### Implementation and Effectivity (IE) Approved
```{r}
nrow(subset(workIE,
            subset = (IEApproved == "A" | IEApproved == "A-FP")))
```

### IE Disapproved
```{r}
nrow(subset(workIE,
            subset = (CRApproved == "D")))
```

## First pass acceptance
### CR
```{r}
nrow(subset(workCR,
            subset = CRApproved == "A-FP")) / 
     nrow(workCR) * 100
```

### IE
```{r}
nrow(subset(workIE,
            subset = IEApproved == "A-FP")) / 
     nrow(workIE) * 100
```

### Total Process
This is the number of data changes that had both the CR and IE approved on first
pass.
```{r}
nrow(subset(work,
            subset = (CRApproved == "A-FP" & IEApproved == "A-FP"))) /
     nrow(work) * 100
```

## Number by Application
### Opened
```{r, eval=FALSE}
table(subset(workCR, 
             subset = CRApproved != "D")$Application)

```

### Completed
```{r, eval=FALSE}
table(subset(workIE, 
             subset = IEApproved != "D")$Application)


```

### Total
```{r, eval=FALSE}
table(subset(workCR, 
             subset = CRApproved != "D")$Application) +
     table(subset(workIE, 
             subset = IEApproved != "D")$Application)

```

## Time to Complete A Data Change
This is the interval between CR approval and IE approval
```{r}
# select from work all that had approved IE for the month
work.all <- subset(work,
                   subset = (IEApproved == "A" | IEApproved == "A-FP"))
# need to figure out a way to make this unique and selected the correct record


# compute interval
work.all$Interval <- as.numeric(work.all$IEDate - work.all$CRDate)
# results
nrow(work.all)
summary(work.all$Interval)
sd(work.all$Interval)
table(work.all$Interval)
quantile(work.all$Interval)
hist(work.all$Interval,
     breaks = 20,
     main = "Histogram of Days to Complete A Change Request",
     xlab = "Day to Complete")
boxplot(work.all$Interval,
        main = "Box Plot of Days to Complete")
boxplot(work.all$Interval,
        main = "Box Plot of Days to Complete With Outliers Removed",
        outline = FALSE)
```

## Number of Days That Currently Open CR Have Been Pending
```{r}
# selected records that have approved CR but no IE
work.open <- subset(ACR,
                    subset = (CRApproved == "A-FP" | CRApproved == "A") & 
                         is.na(IEApproved))
# compute days open                       Set date below to first on next month
work.open$daysOpen <- as.numeric(as.Date("31-Mar-19", 
                                         format = "%d-%b-%y") - 
                                      work.open$CRDate)
# Results
nrow(work.open)
summary(work.open$daysOpen)
sd(work.open$daysOpen)
quantile(work.open$daysOpen)
hist(work.open$daysOpen,
     breaks = 20,
     main = "Histogram of Days Request Open With No IE",
     xlab = "Day to Complete")
boxplot(work.open$daysOpen,
        main = "Box Plot of Days Request Open With No IE")
boxplot(work.open$daysOpen,
        main = "Box Plot of Days Request Open With No IE With Outliers Removed",
        outline = FALSE)
```