---
title: "Exploration"
author: "Nick Lauerman"


output: 
  pdf_document: 
    fig_caption: yes
    fig_height: 7.5
    fig_width: 7.5
    toc: yes
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Purpose
To explore metrics options based on data collected by Software Quality Assurance
in a spreadsheet for document review and approval.

# Libraries used
No libriries used yet
```{r libraries, eval=TRUE}
library(lubridate)
```


# Data
The data is presented n a CVS file (saved from an Excel workbook) with the
following columns and data chartistics

SQA 
: SQAE Preforming the review

Project ID 
: Uniquie ID assigned tot he project may come from NPV or ePAS

Application 
: Application Name (limited selection)

Doc Version 
: Version number of the document, also know as the revision number

Doc ID, if needed 
: unique identifier to distingous between documnets fo the same deliver type 
within a project

Approver or Disapprov?
: Approval status from the following list

* A
: Approved

* A-FP
: Approved on fist pass

* D
: Disapproved

Date of Approval or Disapproval
: Date action was taken

Reason for Disapproval:
Selected from the following list

* Inaccurate information

* Incorrect scope

* Insufficient testing

* Insufficient traceability

* N/A

* Not compliant with procedure

* Not following configuration management

* Not following document version control

* Not using template

* Other

* Requirement deficiency

## Inport the data

The data is read in and variables are assigned more programicaly useful names.
```{r read the data}
FPA.Raw <- read.csv(file = "./data/First Pass Acceptance.csv", 
                    stringsAsFactors = FALSE,
                    col.names = c("sqa",
                                  "project",
                                  "application",
                                  "deliverable",
                                  "version",
                                  "docID",
                                  "status",
                                  "date",
                                  "reason",
                                  "comments"))
FPA <- FPA.Raw
```

## format the data
### factors
Set the following data as factors:

*SQA

*Application

*Deliverable

*status

```{r}
FPA$sqa <- as.factor(FPA$sqa)
FPA$application <- as.factor(FPA$application)
FPA$deliverable <- as.factor(FPA$deliverable)
FPA$status <- as.factor(FPA$status)
```


#### Clean up reason
convert blank fields in status to NA when status is converted to a factor
```{r}
FPA$reason <- as.factor(FPA$reason)
levels(FPA$reason)
levels(FPA$reason)[1] <- NA
levels(FPA$reason)
```

### Date
```{r}
FPA$date <- as.Date(FPA$date, format = "%d-%B-%y")
```

## Add new fields
### Month and year
From date create month and year fields
```{r}
FPA$month <- month(FPA$date, label = TRUE)
FPA$year <- year(FPA$date)
```

## deliverable UID
create an unique identification (UID) for each processed item so that each deliverable
is uniquely identified accross the entire data set. to do this the UID will consist of the
Project, deliverable, docID and version seperated with a dash
```{r}
FPA$UID <- paste(FPA$project,
                  FPA$deliverable,
                  FPA$docID,
                  FPA$version,
                  sep = "-"
                  )
```

# Simple count metrics
## Projects worked
```{r}
length(unique(FPA$project))
as.character(unique(FPA$application))
```

## Number of reviews
```{r}
nrow(FPA)
```

## Number of Documents Reviewed
```{r}
length(unique(FPA$UID))

```


## Number of Projects Started
```{r}
length(unique(
     subset(
          subset(FPA, 
                 subset = ((status == "A" | status == "A-FP") & version == 1)),
          subset = deliverable == "Software Change Request")$project))
```


## Number of Projects Completed
```{r}
length(unique(
     subset(
          subset(FPA, 
                 subset = ((status == "A" | status == "A-FP"))),
          subset = deliverable == "System Certification Summary")$project))
```

## Approval rate
probability of a document being approved when reviewed
```{r}
nrow(unique(
     subset(FPA, subset = (status == "A" | status == "A-FP"))
))/nrow(FPA)

```

## First Pass Acceptance
probability of a document being approved when reviewed the first time
```{r}
nrow(unique(
     subset(FPA, subset = status == "A-FP")
))/nrow(FPA)
```

## Number of deliverables by type
THe number of each type of deliverable 

```{r}
table(FPA[!duplicated(FPA$UID),]$deliverable)
```

## number od deliverable per application
```{r}
table(FPA[!duplicated(FPA$UID),]$application)
```

## distrubation of result of reviews
```{r}
table(FPA$status)
```

