---
title: "Building sample trends for SLC deliverables"
author: "Nick Lauerman"
date: "December 11, 2018"
output: 
  pdf_document: 
    fig_caption: yes
    fig_height: 6.5
    fig_width: 6.5
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo =FALSE}
library(ggplot2)
```

# Load data
The data has been processed and and a dataframe built of the month results
```{r}
load(file = "./data/FPA.RData")
str(FPA)
head(FPA)
```


```{r , echo=FALSE}
FPA$date <- as.Date(paste("1",
                          as.character(FPA$Month),
                          as.character(FPA$Year)), 
                    format = "%d %b %Y")
```

# data overview
```{r, echo=FALSE}
summary(FPA)
```

# Trends
## First pass acceptance
The regression line is included which is showing a downward trend.
Hwever, the analysis indicates a very low probability of corrolation between
date and the FPA rate (8.2%).

```{r, echo=FALSE}
plot(x=FPA$date, y=FPA$First_Pass_Acceptance, 
     type = "b",
     main = "Trend for First Pass Acceptance",
     xlab = "Month",
     ylab = "First Pass Acceptance (%)",
     col = "blue",
     pch = 8)
abline(h=mean(FPA$First_Pass_Acceptance),
       lty = 3)
abline(h=(mean(FPA$First_Pass_Acceptance) + 
              sd(FPA$First_Pass_Acceptance)), 
      lty = 2,
      col = "green")
abline(h=(mean(FPA$First_Pass_Acceptance) - 
              sd(FPA$First_Pass_Acceptance)), 
      lty = 2,
      col = "green")
linear<- lm(FPA$First_Pass_Acceptance ~ FPA$date)
# summary(linear)
abline(a = linear$coefficients[1],
       b = linear$coefficients[2],
       lty = 4,
       col = "red")
legend("topright",
       c("FPA Rate",
         "one standard dev",
         "linear regression"),
       col = c("blue",
               "green",
               "red"),
       lty = c(3, 2, 4),
       pch = c(8,NA,NA),
       cex = 0.5)
```

## Documents reviewed
The regression line is included which is showing a downward trend.
Hwever, the analysis indicates a very low probability of corrolation between
date and the FPA rate (6.2%).

```{r, echo=FALSE}
plot(x=FPA$date, y=FPA$Reviews_Completed,
     type = "b",
     main = "Trend for Documents Reviewed",
     xlab = "Month",
     ylab = "Number of Documents",
     col = "blue",
     pch = 8)
abline(h=mean(FPA$Reviews_Completed),
       lty = 3)
abline(h=(mean(FPA$Reviews_Completed) +
               sd(FPA$Reviews_Completed)),
       lty = 2,
       col = "green")
abline(h=(mean(FPA$Reviews_Completed) -
               sd(FPA$Reviews_Completed)),
       lty = 2,
       col = "green")
linear<- lm(FPA$Reviews_Completed ~ FPA$date)
# summary(linear)
abline(a = linear$coefficients[1],
       b = linear$coefficients[2],
       lty = 4,
       col = "red")
legend("bottomleft",
       c("documents reviewed",
         "one standard dev",
         "linear regression"),
       col = c("blue",
               "green",
               "red"),
       lty = c(3, 2, 4),
       pch = c(8,NA,NA),
       cex = 0.5)

```

## Projects Started
The regression line is included which is showing a downward trend.
Hwever, the analysis indicates a very low probability of corrolation between
date and the FPA rate (1.6%). 

```{r, echo=FALSE}
plot(x=FPA$date, y=FPA$Projects_Started,
     type = "b",
     main = "Trend for Projects Started",
     xlab = "Month",
     ylab = "Number of Projects Started",
     col = "blue",
     pch = 8)
abline(h=mean(FPA$Projects_Started),
       lty = 3)
abline(h=(mean(FPA$Projects_Started) +
               sd(FPA$Projects_Started)),
       lty = 2,
       col = "green")
abline(h=(mean(FPA$Projects_Started) -
               sd(FPA$Projects_Started)),
       lty = 2,
       col = "green")
linear<- lm(FPA$Projects_Started ~ FPA$date)
# summary(linear)
abline(a = linear$coefficients[1],
       b = linear$coefficients[2],
       lty = 4,
       col = "red")
legend("top",
       c("projects started",
         "one standard dev",
         "linear regression"),
       col = c("blue",
               "green",
               "red"),
       lty = c(3, 2, 4),
       pch = c(8,NA,NA),
       cex = 0.5)
```

## Projects Completed
The regression line is included which is showing a downward trend.
Hwever, the analysis indicates a very low probability of corrolation between
date and the FPA rate (2.5%). 

```{r, echo=FALSE}
plot(x = FPA$date, y = FPA$Projects_Completed,
     type = "b",
     main = "Trend for Projects Completed",
     xlab = "Month",
     ylab = "Number of Projects Completed",
     col = "blue",
     pch = 8)
abline(h=mean(FPA$Projects_Completed),
       lty = 3)
abline(h=(mean(FPA$Projects_Completed) +
               sd(FPA$Projects_Completed)),
       lty = 2,
       col = "green")
abline(h=(mean(FPA$Projects_Completed) -
               sd(FPA$Projects_Completed)),
       lty = 2,
       col = "green")
linear<- lm(FPA$Projects_Completed ~ FPA$date)
# summary(linear)
abline(a = linear$coefficients[1],
       b = linear$coefficients[2],
       lty = 4,
       col = "red")
legend("top",
       c("projects completed",
         "one standard dev",
         "linear regression"),
       col = c("blue",
               "green",
               "red"),
       lty = c(3, 2, 4),
       pch = c(8,NA,NA),
       cex = 0.5)

```


