---
title: "Functions"
author: "Nick Lauerman"
output: 
  pdf_document: 
    fig_caption: yes
    fig_height: 7.5
    fig_width: 7.5
    toc: yes
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Last Run 23 Jan 2018 @ 10:17

This is to document the develpoment of functins derived from various other
activities to support the FPA proejct. It is important to note tha functions
developed or documente here will have to be included in an R file so they may be
easily brought into the R enviroment in the future.

# Data Input
this function will read the csv file in and will make required conversions to factors
or date
```{r}
get.FPA <- function(file = "./data/First Pass Acceptance.csv", month = NULL){
     FPA <- read.csv( file = file, 
                      stringsAsFactors = FALSE,
                      col.names = c("sqa",
                                    "project",
                                    "application",
                                    "deliverable",
                                    "version",
                                    "docID",
                                    "status",
                                    "date",
                                    "reason",
                                    "comments"))
}

```

## Test
### count
First the fuctin is run creating the FPA data frame. The the number of rows in the 
data frame is checked again the source data (66 at this time) as well as the number 
of columns (10)
```{r}
FPA <- get.FPA()
nrow(FPA)
ncol(FPA)
dim(FPA)
str(FPA)
```

# cleaning Data
## Factors and Date
```{r}
clean.FPA <- function(FPA){
     require(lubridate)
     FPA$sqa <- as.factor(FPA$sqa)
     FPA$application <- as.factor(FPA$application)
     FPA$deliverable <- as.factor(FPA$deliverable)
     FPA$status <- as.factor(FPA$status)
     FPA$reason <- as.factor(FPA$reason)
     levels(FPA$reason)[1] <- NA
     FPA$date <- as.Date(FPA$date, format = "%d-%B-%y")
     return(FPA)
}
```

### Test
Now a count of each factor will be tabulated to verify against the know data and 
look at data frame structure
```{r}
FPA <- clean.FPA(FPA = FPA)
str(FPA)
table(FPA$sqa)
table(FPA$application)
table(FPA$deliverable)
table(FPA$status)
table(FPA$reason)
table(FPA$date)
```

# Processing

Create a seperate value for Month and Year for the date value.

Create a UID for each deliverable
```{r}
process <- function(FPA){
     require(lubridate)
     FPA$month <- month(FPA$date, label = TRUE)
     FPA$year <- year(FPA$date)
     FPA$UID <- paste(FPA$project,
                      FPA$deliverable,
                      FPA$docID,
                      FPA$version,
                      sep = "-")
}
```

## Test
inspect the structor of the data frame
```{r}
str(FPA)
```

Now look at at the new values
```{r}
table(FPA$month)
table(FPA$year)
table((FPA$UID))
```



