---
title: "Functions"
author: "Nick Lauerman"
date: "January 22, 2018 @ 4:00 PM"
output: 
  pdf_document: 
    fig_caption: yes
    fig_height: 7.5
    fig_width: 7.5
    toc: yes
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is to document the develpoment of functins derived from various other
activities to support the FPA proejct. It is important to note tha functions
developed or documente here will have to be included in an R file so they may be
easily brought into the R enviroment in the future.

# Data Input
this function will read the csv file in and will make required conversions to factors
or date
```{r}
get.csv <- function(file = "./data/First Pass Acceptance.csv", month = NULL){
     FPA <- read.csv( file = file, 
                      stringsAsFactors = FALSE,
                      col.names = c("sqa",
                                    "project",
                                    "application",
                                    "deliverable",
                                    "version",
                                    "docID",
                                    "status",
                                    "date",
                                    "reason",
                                    "comments"))
     FPA$sqa <- as.factor(FPA$sqa)
     FPA$application <- as.factor(FPA$application)
     FPA$deliverable <- as.factor(FPA$deliverable)
     FPA$status <- as.factor(FPA$status)
     FPA$reason <- as.factor(FPA$reason)
     levels(FPA$reason)[1] <- NA
     FPA$date <- as.Date(FPA$date, format = "%d-%B-%y")
     return(FPA)
}
```

## Test
### count
First the fuctin is run creating the FPA data frame. The the number of rows in the 
data frame is checked again the source data (66 at this time) as well as the number 
of columns (10)
```{r}
FPA <- get.csv()
nrow(FPA)
ncol(FPA)
dim(FPA)
```

### Factors and Date
Now a count of each factor will be tabulated to verify against the know data
```{r}
table(FPA$sqa)
table(FPA$application)
table(FPA$deliverable)
table(FPA$status)
table(FPA$reason)
table(FPA$date)
```


